Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-11-17 inst/examples/20170201-manuscript.Rmd
ok

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "20170201_manuscript/", dpi = 300)
knitr::opts_chunk$set(dev = c("png", "jpeg"))
#knitr::opts_chunk$set(dev = "cairo_pdf") # Embed fonts
#knitr::opts_chunk$set(dev = "cairo_ps") # Embed fonts
# knitr::opts_chunk$set(dev = c("png")) # Embed fonts
knitr::opts_chunk$set(out.width = "10cm") # Default size 8.5cm ie 3.35 inch) per col
knitr::opts_chunk$set(out.format = "latex")

@@

```{r Figure_1, message=FALSE, warning=FALSE, fig.width=11, fig.height=5, echo=FALSE}

>>>>

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "20170201_manuscript/", dpi = 300)
knitr::opts_chunk$set(dev = c("png", "jpeg", "cairo_ps"))
#knitr::opts_chunk$set(dev = "cairo_pdf") # Embed fonts
#knitr::opts_chunk$set(dev = "cairo_ps") # Embed fonts
knitr::opts_chunk$set(out.width = "17cm") # Default size 8.5cm ie 3.35 inch) per col
knitr::opts_chunk$set(out.format = "latex")

@@

```{r Figure_1, message=FALSE, warning=FALSE, fig.width=13, fig.height=5, echo=FALSE}
